---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aFILLiator

<!-- badges: start -->
<!-- badges: end -->

aFILLiator is a small collection of scripts that find the affiliation of an author by looking at the affiliation they used in their last paper available in [PubMed](https://pubmed.ncbi.nlm.nih.gov/). The goal is to help authors to find the affiliations of their collaborators, thus speeding up the writing process of this tedious (but necessary) section.

## Installation

You can install the development version of aFILLiator from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Benjamin-Valderrama/aFILLiator")
```

## Example

This is a basic example which shows you how aFILLiator works...

```{r minimal example}
library(aFILLiator)

# we call the main function of aFILLiator
aFILLiator(fore_name = "Benjamin", last_name = "Valderrama")

```

aFILLiator also supports working with multiple authors as long as they are provided as data frame with two columns, one with forenames `fore_names` and the other with last names `last_name`.

```{r preparing data frame, include=FALSE}

test_df <- data.frame(fore_name = c("Thomaz", "Benjamin", "John F"),
                      last_name = c("Bastiaanssen", "Valderrama" , "Cryan"))


```

```{r data frame example}

library(aFILLiator)

# Example data frame
test_df

# convert to a list to loop over it
names_list <- test_df |> 
        as.list()

# loop over the matching forenames and last names using the aFILLliator function
affiliations_df <- mapply(aFILLiator, names_list$fore_name, names_list$last_name) |>
        t() |>
        data.frame() |>
        # make the output a data frame again
        sapply(X = _, FUN = unlist) |>
        data.frame()


# see the output
affiliations_df

```
